Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-09 method.tex
start to describe the philosophy
scratch

core of the paper: agent simulation, decision making.

@@

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}
matching the 
\begin{figure}

\begin{tikzpicture}
\begin{class}[text width=8cm]{Job}{0,0}
    \attribute{needCapacity : Map}
    \operation{lala(haha): void}
\end{class}
\end{tikzpicture}
\caption{Test UML Diagram}

\end{figure}
% subsubsection platform_agent (end)

@@

\subsubsection{Design philosopher} % (fold)
\label{ssub:design_philosopher}
platform create demander and provider
demander, a subclass of user, generate need i.e. create order (the defined task bunch)
    task is a subclass of job, need to be processed with specified resource type and amount(type,amount) , have its process time.
provider, a subclass of user, provider resource with different type and capacity, these resources can be allocated to task job and service-call job, service-call is subclass of job, which is the job to combined to create service.

@@

% subsubsection design_philosopher (end)

@@

Decision making involves choosing some course of action among various alternatives. For a decision maker, fulfilling the con

@@

\subsection{Agent-based modeling and simulation} % (fold)
\label{sub:agent_based_modeling_and_simulation}
\subsubsection{Agent design}

\subsubsection{Logical process}

\subsubsection{Interaction among agents}
some mathematical formulation display here to describe the whole ecosystem wide phenomenon, like Little formulation.

>>>>

core of the paper: agent simulation, decision-making.

@@

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}

% subsubsection platform_agent (end)

@@

\subsubsection{Design philosophy} % (fold)
\label{ssub:design_philosophy}
platform create demander and provider
demander, a subclass of user, generate need i.e. create order (the defined task bunch)
    task is a subclass of job, need to be processed with specified resource type and amount(type,amount) , have its process time.
provider, a subclass of user, provider resource with different type and capacity, these resources can be allocated to task job and service-call job, service-call is subclass of job, which is the job to combined to create service.

@@

% subsubsection design_philosophy (end)

@@

Decision-making involves choosing some course of action among various alternatives. For a decision maker, fulfilling the con

@@

\subsection{Agent-based modeling and simulation} % (fold)
\label{sub:agent_based_modeling_and_simulation}
\subsubsection{Agent Classes}
\begin{asparaenum}
\item User related
\suspend{asparaenum}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/cUser}
    \input{figures/cProvider}
\input{figures/cDemander}
    \end{tikzpicture}
    \caption{User related classes}
    \label{fig:userclassed}
\end{figure}
\resume{asparaenum}
\item Job related
\suspend{asparaenum}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/cJob}
    \input{figures/cTask}
    \input{figures/cServiceCall}
    \end{tikzpicture}
    \caption{Job related classes}
    \label{fig:jobclassed}
\end{figure}
\resume{asparaenum}
\item Machine related
\end{asparaenum}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/cMachine}
    \input{figures/cResource}
    \input{figures/cService}
    \end{tikzpicture}
    \caption{Machine related classes}
    \label{fig:machineclassed}
\end{figure}
\subsubsection{Behavior interface and classes}
\begin{asparaenum}
\item Assign behavior
\suspend{asparaenum}
\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/iAssignBehavior}
    \input{figures/cServiceAssign}
    \input{figures/cResourceAssign}
    \end{tikzpicture}
    \caption{Assign interface and related classes}
    \label{fig:assigninterface}
\end{figure}

\resume{asparaenum}
\item Process behavior
\suspend{asparaenum}

\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/iProcessBehavior}
    \input{figures/cProcessInTask}
    \input{figures/cProcessInServiceCall}
    \end{tikzpicture}
    \caption{Process interface and related classes}
    \label{fig:processinterface}
\end{figure}
\resume{asparaenum}
\item Release behavior
\suspend{asparaenum}

\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/iReleaseBehavior}
    \input{figures/cResourceRelease}
    \input{figures/cServiceRelease}
    \end{tikzpicture}
    \caption{Release interface and related classes}
    \label{fig:releaseinterface}
\end{figure}
\resume{asparaenum}
\item Response behavior
\suspend{asparaenum}

\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/iResponseBehavior}
    \input{figures/cResourceResponse}
    \input{figures/cServiceResponse}
    \end{tikzpicture}
    \caption{Response interface and related classes}
    \label{fig:reponseinterface}
\end{figure}
\resume{asparaenum}
\item Select behavior
\end{asparaenum}

\begin{figure}[htbp]
    \centering
    \scriptsize
    \begin{tikzpicture}
    \input{figures/iSelectBehavior}
    \input{figures/cSelectInTask}
    \input{figures/cSelectInServiceCall}
    \end{tikzpicture}
    \caption{Select interface and related classes}
    \label{fig:selectinterface}
\end{figure}
\subsubsection{Interaction among agents}
some mathematical formulation display here to describe the whole ecosystem wide phenomenon, like Little formulation.

### 2016-09-09 result.tex
modify the abstract

Individuals in the manufacturing ecosystem are: \begin{inparaenum}[1)]
\item autonomous and self-directed, 
\item social, interacting with other entities, 
\item controlled by the environment, 
\item self-contained.
\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study in such complex system. With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments with it.

@@

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}. 
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%
We assume provider and demander are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, and we make sure that:
\begin{equation}
\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
\end{equation}

@@

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.eps}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ means that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}

% subsubsection result_and_analysis (end)

>>>>

Individuals in the manufacturing ecosystem are: \begin{inparaenum}[1)]
\item autonomous and self-directed,
\item social, interacting with other entities,
\item controlled by the environment,
\item self-contained.
\end{inparaenum} They optimize their multi-objective decision-makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique \cite{Macal2009,north2007managing} is suitable for the study in such a complex system. With the help of Repast Simphony \cite{North2013} package was utilized in this experiment.

@@

\subsection{Experiments} % (fold)
\label{ssub:case_design}
RanGen \cite{Demeulemeester2003} was used to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%
We assume that providers and demanders are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the average coming resource capacity rate in average to prevent the task explosion, and we make sure that,
\begin{equation}
\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
\end{equation}

@@

\subsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}
Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.  After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
\begin{table}[htbp]
    \caption{Average observed values}
    \label{tab:averagevalue}
    \centering
    \scriptsize
    \begin{tabular}{lccccc}
    \toprule
    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
    \midrule
    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{asparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22. Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22.
\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ means that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
\item There is no big difference among all the 6 modes in rank change. Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by. Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
\end{asparaenum}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{Data/out.eps}
    \caption{Observed variable change with time}
    \label{fig:out}
\end{figure}
% subsubsection result_and_analysis (end)
